Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-03-22 Paper/Manuscript.tex
Move two more refs to using citep

Recent echosounders produce pulses with a wide and continuous frequency range (broadband pulses), as opposed to conventional single frequency systems, i.e. a continuous frequency coverage over a wide frequency band. This provides significantly better along-beam resolution and a higher signal to noise ratio than narrowband pulses \citep{Chu1998Application, ehrenbergFMSlideChirp2000}. These benefits can lead to improved backscatter categorization \citep{korneliussen2018, Traykovski1998Effect, Stanton2012Resonance, Korneliussen2016Acoustic} and hence more accurate distribution and abundance estimates, as well as enhanced information on ecosystem structure and functioning. Early work with recent commercial systems indicate the potential improvement in detection near boundaries \citep{lavery2017} and remote sizing of fish \citep{kubilius_remote_2020}, capabilities of fine-scale observations of interactions between prey and predators \citep{skaret_diel_2020}, the potential for species discrimination \citep{bassett_broadband_2018, blanluet_characterization_2019, benoit-bird_exploring_2020} (+Hasegawa et al., 2021; Gugele et al., 2021), and the potential for enhanced information on mesopelagic layers \citep{cotter_classification_2021, agersted_application_2021, khodabandeloo_estimating_2021, khodabandeloo_mesopelagic_2021}.

>>>>

Recent echosounders produce pulses with a wide and continuous frequency range (broadband pulses), as opposed to conventional single frequency systems, i.e. a continuous frequency coverage over a wide frequency band. This provides significantly better along-beam resolution and a higher signal to noise ratio than narrowband pulses \citep{Chu1998Application, ehrenbergFMSlideChirp2000}. These benefits can lead to improved backscatter categorization \citep{korneliussen2018, Traykovski1998Effect, Stanton2012Resonance, Korneliussen2016Acoustic} and hence more accurate distribution and abundance estimates, as well as enhanced information on ecosystem structure and functioning. Early work with recent commercial systems indicate the potential improvement in detection near boundaries \citep{lavery2017} and remote sizing of fish \citep{kubilius_remote_2020}, capabilities of fine-scale observations of interactions between prey and predators \citep{skaret_diel_2020}, the potential for species discrimination \citep{bassett_broadband_2018, blanluet_characterization_2019, benoit-bird_exploring_2020, gugele_differentiation_2021, hasegawa_situ_2021}, and the potential for enhanced information on mesopelagic layers \citep{cotter_classification_2021, agersted_application_2021, khodabandeloo_estimating_2021, khodabandeloo_mesopelagic_2021}.
